---
title: "gridder-vignette"
author: Xiao Feng, Tainá Rocha, ....
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gridder-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

 
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Add Image Logo
 
 __GridDER__ Grid Detection and Evaluation in R a tool for identifying biodiversity records that have been designated locations on widely used grid systems. Our tool also estimates the degree of environmental heterogeneity associated with grid systems, allowing users to make informed decisions about how to use such occurrence data in global change studies.
 
 # Installing

Currently __GridDER__ can be installed from GitHub:

```{r install, eval = F}
remotes::install_github("BiogeographyLab/gridder",
                        auth_token = "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")

```

##  The example dataset

__GridDER__ comes with example data, a list called `occ_grid_id_9` with
occurrence data derive3d from grid system, and some grid systems called
`grid_ID_2_polygon_masked` and `grid_ID_9` .

```{r}
library(gridder)
```


